### 2022-12-12 paper4.tex
formatting

We will illustrate the application of \eqref{eq4:prior-precision} and
\eqref{eq4:prior-mean} as well as the methodology in the rest of this paper
using a recent meta-analysis combining information from $n=7$ randomized
controlled trials investigating the association between corticosteroids and
mortality in hospitalized patients with COVID-19 \citep{REACT2020}; its results
are reproduced in Figure \ref{fig4:covid19-meta} (here and henceforth, odds
ratios (ORs) are expressed as log odds ratios to transform the range from
$(0, \infty)$ to $(-\infty, +\infty)$, consistent with the assumption of
normality). Let $x_i = \hat \theta_i$ denote the maximum likelihood estimate
(MLE) of the log odds ratio $\theta$ in the $i$-th study with standard error
$\sigma_i$. The meta-analytic odds ratio estimate under the fixed-effect model
(the pre-specified primary analysis) is $\widehat{\text{OR}} = 0.66$ [95\% CI
$0.53$ to $0.82$], respectively $\hat \theta = -0.42$ [95\% CI $-0.63$ to
$-0.20$] for the log odds ratio $\theta$, indicating evidence for lower
mortality of patients treated with corticosteroids compared to patients
receiving usual care or placebo. The pooled effect estimate $\hat \theta$
represents a posterior mean $\mu'$ with posterior precision $\delta'=83.8$.

@@

It is also possible to apply the approach to the meta-analytic log odds ratio
estimate $\hat \theta = -0.42$ [95\% CI $-0.63$ to $-0.20$] from all 7 studies
combined. Then $\SL= 0.13$, so the meta-analytic estimate can be considered as
non-credible if external evidence suggests that mortality reductions are
unlikely to exceed $1-\exp(-\SL)=1 - 0.88 \approx 12 \%$. This illustrates that
the meta-analytic estimate has gained credibility compared to the result from
the RECOVERY study alone, despite the reduction in the effect estimate
($\widehat{\text{OR}} = \exp(\hat \theta) = 0.66$ vs.~0.59 in the RECOVERY
study).

@@

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/AnCred-examples-plot-1}
}
\end{knitrout}
\caption{Two examples of the Analysis of Credibility. Shown are point estimates
  within 95\% confidence/credible intervals. The left plot illustrates how a
  sceptical prior is used to challenge the significant finding from the RECOVERY
  trial \citep{RECOVERY2020}. The right plot illustrates how an advocacy prior
  is used to challenge a non-significant finding from the REMAP-CAP trial
  \citep{REMAPCAP2020}. In both scenarios the posterior is fixed to be just
  non-credible/credible.}
\label{fig4:anCredEx}
\end{figure}

For illustration we consider the data from the REMAP-CAP trial that supported
the RECOVERY trial finding of decreased COVID-19 mortality from corticosteroid
use. However, this trial involved far fewer patients, and despite the point
estimate showing efficacy, the relatively large uncertainty rendered the overall
finding non-significant at the 5\% level ($\hat{\theta} = -0.34$ [95\% CI
$-0.96$ to $0.29$]). Such an outcome is frequently (and wrongly) taken to imply
no effect. The use of AnCred leads to a more nuanced conclusion. The advocacy
limit AL on the log odds ratio scale for REMAP-CAP is $-1.89$, \ie{} $0.15$ on the
odds ratio scale, see also the right plot in Figure \ref{fig4:anCredEx}. Thus
advocates of the effectiveness of corticosteroids can regard the trial as
providing credible evidence of effectiveness despite its non-significance if
external evidence supports mortality reductions (in terms of odds) in the range
0\% to 85\%. So broad an advocacy range reflects the fact that this relatively
small trial provides only modest evidential weight, and thus little constraint
on prior beliefs about the effectiveness of corticosteroids.

@@

While the assumption of large studies can be appropriate with epidemiological
studies involving rare events, it can be harder to justify for RCTs.
Fortunately, the theory can be extended to encompass these and also the case of
non-significant findings with little additional complexity. In the case of the
sceptical prior, we simply require that the numbers of event $m$ and non-events
$n$ are the same in both arms to constrain the mean to zero; the variance
\eqref{eq4:SElogOR} then simplifies to $2/m + 2/n$. Adding the constraint that
the event rate of the sceptical prior $R= m /(m + n)$ matches that of the study
under assessment, we then find
\begin{eqnarray*}
  m = \frac{2}{\tau^{2}(1 - R)} & \mbox{ and }
  &n = \frac{m(1 - R)}{R}.
\end{eqnarray*}
For example, from Figure~\ref{fig4:covid19-meta} the RECOVERY trial has an
overall mortality rate $R=(95 + 283)/(324 + 683) = 37.54\%$ and $\SL = 0.178$ at
the $\alpha = 5\%$ level $(z_{\alpha/2} = 1.96)$ corresponds to
$\tau^2=0.091^2$, so $m = 389$ and $n = 648$ (these are integer approximations
of exact computations), and thus a prior study capable of challenging the
credibility of the RECOVERY trial requires $1037$ patients and $389$ deaths in
each arm. At more than twice the size of the RECOVERY trial ($2074$ vs. $1007$)
patients and considerably more deaths in both arms, this level of sceptical
prior evidence highlights the robustness of the trial finding.

A similar approach determines the characteristics of the hypothetical prior
study needed to turn a ``negative'' non-significant finding into one that is
credible to a specific $\alpha$ level. The Reverse-Bayes advocacy prior from
\citet{Matthews2018} described in Section~\ref{sec4:nonSigAnCred} has a mean
$\mu = \mbox{AL}/2$ and variance $\tau^{2} = \AL^2/(2z_{\alpha/2})^2$. Under the
large study assumption and equating the latter with \eqref{eq4:SElogOR} as
before, the corresponding number of events needed to be observed in both arms of
the hypothetical study is $m = 2/\tau^{2} = 8 \, z_{\alpha/2}^2/\mbox{AL}^2$. To
incorporate the non-zero mean by which this prior represents advocacy, these $m$
events are taken to have been observed among participants allocated to the two
study arms in the ratio $1 \colon K$ where $K = \exp(\mu) = \exp(\AL/2)$, the
allocation being such that it increases the relative evidential weight for the
hypothesis ``negated'' by the non-significance.

@@

Reporting of minimum Bayes factors is one attempt of solving the Problem of
Priors in Bayesian inference. However, this bound may be rather small and the
corresponding prior unrealistic. In contrast, the Reverse-Bayes approach makes
the choice of the prior explicit by determining the relative prior variance
parameter $g$ such that the finding is no longer compelling, followed by
assessing the plausibility of this prior. To do so, one first fixes
$\BF_{01} = \gamma$, where $\gamma$ is a cut-off above which the result is no
longer convincing, for example $\gamma = 1/10$, the level for strong evidence
according to the classification from \citet{Jeffreys1961}. The sufficiently
sceptical relative prior variance is then given by
\begin{align}
\label{ggamma}
  g &=
  \begin{cases}
    -\dfrac{z^2}{q} - 1
    & ~~ \text{if} ~
    -\dfrac{z^2}{q} \geq 1 \\
    \text{undefined} & ~~ \text{else}
  \end{cases} \\
  \text{where} ~ q &=
  \text{W} \left(-\frac{z^2}{\gamma^2} \cdot
  \exp\left\{-z^2\right\}\right)
  \nonumber
\end{align}
where $\text{W}(\cdot)$ is the branch of the Lambert $W$ function that satisfies
$text{W}(y) \leq -1$ for $y \in [-e^{-1}, 0)$ \citep{Corless1996}, see the
Appendix in \citep{Pawel2020b} for a proof.

@@

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/AnCred-BF-examples-plot-1}
}
\end{knitrout}
\caption{Illustration of the AnCred with Bayes factors procedure using the
  findings from the meta-analysis on the association of COVID-19 mortality and
  corticosteroids. The left plot shows the Bayes factor $\BF_{01}$ as a function
  of the relative variance $g$ of the sceptical prior. The result from the
  RECOVERY trial is challenged with a sceptical prior such that
  $\BF_{01} = 1/10$, for the other trials such a prior does not exist. The right
  plot shows the Bayes factor $\BF_{01}$ as a function of the relative mean
  $f = \mu/\hat{\theta}$ of the advocacy prior where the coefficient of
  variation from the prior is fixed to
  $\text{CV} = \tau/\mu = 1/z(\gamma=1/3) = 0.67$, where $z(\gamma)$ is given in
  \eqref{eq4:zgamma}. The RECOVERY and the CAPE COVID findings are challenged
  such that $\BF_{01} = 1/3$, for the other trials such a prior does not exist.}
\label{fig4:bf}
\end{figure}

@@

The plausibility of the sufficiently sceptical prior can be evaluated in light
of external evidence, but what should we do in the absence of such? We could
again use the \citet{Box1980} prior-predictive check as in
Section~\ref{sec4:IC}, however, the resulting tail probability is difficult to
compare to the Bayes-factor cut-off $\gamma$. When a specific alternative model
to the null is in mind, \citet[p. 391]{Box1980} also suggested to use a Bayes
factor for model criticism of the null model. Following this approach,
\citet{Pawel2020b} proposed to define a second Bayes factor contrasting the
sufficiently sceptical prior to an optimistic prior, which they defined as
$\theta \given H_2 \sim \Nor(\hat{\theta}, \sigma^2)$ the posterior of $\theta$
based on the data and the reference prior $f(\theta) \propto 1$. The optimistic
prior therefore represents the position of a proponent who takes the original
claim at face value. This leads to the second Bayes factor being
\begin{align}
  \label{eq4:bf12}
  \BF_{12} = \sqrt{\frac{2}{1 + g}} \cdot \exp\left\{-\frac{1}{2}\cdot \frac{z^{2}}{1 + g}\right\}.
\end{align}
Analogously to the tail probability approach from Section~\ref{sec4:IC},
intrinsic credibility is established if the data support the optimistic over the
sceptical prior at a higher level than they support the sceptical prior over the
null hypothesis, \ie{} if
\begin{align*}
  \BF_{12} \leq \BF_{01}
\end{align*}
with sufficiently sceptical relative prior variance $g$ from~\eqref{ggamma} used
in both Bayes factors. For example, if we challenge the RECOVERY trial finding
such that the resulting Bayes factor is only $\BF_{01} = 1/10$, we obtain
with~\eqref{eq4:sspv} the sufficiently sceptical relative prior variance
$g = 0.59$ and in turn with~\eqref{eq4:bf12} the Bayes factor $\BF_{12} = 1/64$,
so the finding is intrinsically credible at $\gamma = 1/10$.

@@

The right plot in Figure \ref{fig4:bf} illustrates application of the procedure
on data from the meta-analysis on association between COVID-19 mortality and
corticosteroids. The coefficient of variation of the advocacy prior is fixed to
$\text{CV} = 1/z(\gamma=1/3) = 0.67$ (for comparison, the CV of the advocacy
prior in traditional AnCred at $\alpha = 0.05$ is
$\text{CV} = 1/z_{\alpha/2}= 0.51$) and thus the Bayes factor $\BF_{01}$ only
depends on the relative mean $f = \mu/\hat{\theta}$. Under the sceptical prior
only the RECOVERY finding could be challenged at $\gamma = 1/3$ (where
$z(\gamma)=1.5$ corresponds to $\alpha=13$\%). With the advocacy prior this is
now also possible for the CAPE COVID finding \citep{Dequin2020}, where a prior
with mean $\mu = f \cdot \hat{\theta} = 0.37 \cdot (-0.79) = -0.29$ and standard
deviation $\tau = \text{CV} \cdot \mu = 0.2$ is able to make the finding
compelling at $\gamma = 1/3$. The corresponding prior credible interval for the
OR at level $1-\alpha$ ranges from 0.55 to 1, so advocates may still consider
the ``non-compelling'' finding as providing moderate evidence in favour of a
benefit, if external evidence supports mortality reductions in that range. Using
the prior-to-data conversion described in
Section~\ref{sec4:prior-data-translation}, the prior can be translated to a
trial with 69 events in both arms, but 206 non-events in the treatment and 182
non-events in the control arm (such that the mortality rate in the control arm
is the same as in the CAPE-COVID trial). Note that the advocacy prior may not be
unique, \eg{} for the CAPE COVID finding the prior with relative mean
$f^\prime = 1.26$ and standard deviation $\tau^\prime = 0.67$ also renders the
data as just compelling at $\gamma = 1/3$. We recommend to choose the prior with
$f$ closer to zero, as it is the more conservative choice.

>>>>

We will illustrate the application of \eqref{eq4:prior-precision} and
\eqref{eq4:prior-mean} as well as the methodology in the rest of this paper
using a recent meta-analysis combining information from $n=7$ randomized
controlled trials investigating the association between corticosteroids and
mortality in hospitalized patients with COVID-19 \citep{REACT2020}; its results
are reproduced in Figure \ref{fig4:covid19-meta} (here and henceforth, odds
ratios (ORs) are expressed as log odds ratios to transform the range from
$(0, \infty)$ to $(-\infty, +\infty)$, consistent with the assumption of
normality). Let $x_i = \hat \theta_i$ denote the maximum likelihood estimate
(MLE) of the log odds ratio $\theta$ in the $i$-th study with standard error
$\sigma_i$. The meta-analytic odds ratio estimate under the fixed-effect model
(the pre-specified primary analysis) is \mbox{$\widehat{\text{OR}} = 0.66$ [95\%
  CI $0.53$ to $0.82$]}, respectively \mbox{$\hat \theta = -0.42$ [95\% CI
  $-0.63$ to $-0.20$]} for the log odds ratio $\theta$, indicating evidence for
lower mortality of patients treated with corticosteroids compared to patients
receiving usual care or placebo. The pooled effect estimate $\hat \theta$
represents a posterior mean $\mu'$ with posterior precision $\delta'=83.8$.

@@

It is also possible to apply the approach to the meta-analytic log odds ratio
estimate \mbox{$\hat \theta = -0.42$ [95\% CI $-0.63$ to $-0.20$]} from all 7
studies combined. Then $\SL= 0.13$, so the meta-analytic estimate can be
considered as non-credible if external evidence suggests that mortality
reductions are unlikely to exceed $1-\exp(-\SL)=1 - 0.88 \approx 12 \%$. This
illustrates that the meta-analytic estimate has gained credibility compared to
the result from the \mbox{RECOVERY} study alone, despite the reduction in the
effect estimate ($\widehat{\text{OR}} = \exp(\hat \theta) = 0.66$ vs.~0.59 in
the RECOVERY study).

@@

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/AnCred-examples-plot-1}
}
\end{knitrout}
\caption{Two examples of the Analysis of Credibility. Shown are point estimates
  within 95\% confidence/credible intervals. The left plot illustrates how a
  sceptical prior is used to challenge the significant finding from the RECOVERY
  trial \citep{RECOVERY2020}. The right plot illustrates how an advocacy prior
  is used to challenge a non-significant finding from the \mbox{REMAP-CAP} trial
  \citep{REMAPCAP2020}. In both scenarios the posterior is fixed to be just
  non-credible/credible.}
\label{fig4:anCredEx}
\end{figure}

For illustration we consider the data from the REMAP-CAP trial that supported
the RECOVERY trial finding of decreased COVID-19 mortality from corticosteroid
use. However, this trial involved far fewer patients, and despite the point
estimate showing efficacy, the relatively large uncertainty rendered the overall
finding non-significant at the 5\% level (\mbox{$\hat{\theta} = -0.34$ [95\% CI
  $-0.96$ to $0.29$]}). Such an outcome is frequently (and wrongly) taken to
imply no effect. The use of AnCred leads to a more nuanced conclusion. The
advocacy limit AL on the log odds ratio scale for REMAP-CAP is $-1.89$, \ie{}
$0.15$ on the odds ratio scale, see also the right plot in Figure
\ref{fig4:anCredEx}. Thus advocates of the effectiveness of corticosteroids can
regard the trial as providing credible evidence of effectiveness despite its
non-significance if external evidence supports mortality reductions (in terms of
odds) in the range 0\% to 85\%. So broad an advocacy range reflects the fact
that this relatively small trial provides only modest evidential weight, and
thus little constraint on prior beliefs about the effectiveness of
corticosteroids.

@@

While the assumption of large studies can be appropriate with epidemiological
studies involving rare events, it can be harder to justify for RCTs.
Fortunately, the theory can be extended to encompass these and also the case of
non-significant findings with little additional complexity. In the case of the
sceptical prior, we simply require that the numbers of event $m$ and non-events
$n$ are the same in both arms to constrain the mean to zero; the variance
\eqref{eq4:SElogOR} then simplifies to $2/m + 2/n$. Adding the constraint that
the event rate of the sceptical prior $R= m /(m + n)$ matches that of the study
under assessment, we then find
\begin{eqnarray*}
  m = \frac{2}{\tau^{2}(1 - R)} & \mbox{ and }
  &n = \frac{m(1 - R)}{R}.
\end{eqnarray*}
For example, from Figure~\ref{fig4:covid19-meta} the RECOVERY trial has an
overall mortality rate \mbox{$R=(95 + 283)/(324 + 683) = 37.54\%$} and
$\SL = 0.178$ at the $\alpha = 5\%$ level $(z_{\alpha/2} = 1.96)$ corresponds to
$\tau^2=0.091^2$, so $m = 389$ and $n = 648$ (these are integer approximations
of exact computations), and thus a prior study capable of challenging the
credibility of the RECOVERY trial requires $1037$ patients and $389$ deaths in
each arm. At more than twice the size of the RECOVERY trial ($2074$ vs. $1007$)
patients and considerably more deaths in both arms, this level of sceptical
prior evidence highlights the robustness of the trial finding.

A similar approach determines the characteristics of the hypothetical prior
study needed to turn a ``negative'' non-significant finding into one that is
credible to a specific $\alpha$ level. The Reverse-Bayes advocacy prior from
\citet{Matthews2018} described in Section~\ref{sec4:nonSigAnCred} has a mean
\mbox{$\mu = \mbox{AL}/2$} and variance $\tau^{2} = \AL^2/(2z_{\alpha/2})^2$.
Under the large study assumption and equating the latter with
\eqref{eq4:SElogOR} as before, the corresponding number of events needed to be
observed in both arms of the hypothetical study is
$m = 2/\tau^{2} = 8 \, z_{\alpha/2}^2/\mbox{AL}^2$. To incorporate the non-zero
mean by which this prior represents advocacy, these $m$ events are taken to have
been observed among participants allocated to the two study arms in the ratio
$1 \colon K$ where \mbox{$K = \exp(\mu) = \exp(\AL/2)$}, the allocation being
such that it increases the relative evidential weight for the hypothesis
``negated'' by the non-significance.

@@

Reporting of minimum Bayes factors is one attempt of solving the Problem of
Priors in Bayesian inference. However, this bound may be rather small and the
corresponding prior unrealistic. In contrast, the Reverse-Bayes approach makes
the choice of the prior explicit by determining the relative prior variance
parameter $g$ such that the finding is no longer compelling, followed by
assessing the plausibility of this prior. To do so, one first fixes
$\BF_{01} = \gamma$, where $\gamma$ is a cut-off above which the result is no
longer convincing, for example $\gamma = 1/10$, the level for strong evidence
according to the classification from \citet{Jeffreys1961}. The sufficiently
sceptical relative prior variance is then given by
\begin{align}
\label{ggamma}
  g &=
  \begin{cases}
    -\dfrac{z^2}{q} - 1
    & ~~ \text{if} ~
    -\dfrac{z^2}{q} \geq 1 \\
    \text{undefined} & ~~ \text{else}
  \end{cases} \\
  \text{where} ~ q &=
  \text{W} \left(-\frac{z^2}{\gamma^2} \cdot
  \exp\left\{-z^2\right\}\right)
  \nonumber
\end{align}
where $\text{W}(\cdot)$ is the branch of the Lambert $W$ function that satisfies
$\text{W}(y) \leq -1$ for \mbox{$y \in [-e^{-1}, 0)$} \citep{Corless1996}, see the
Appendix in \citep{Pawel2020b} for a proof.

@@

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/AnCred-BF-examples-plot-1}
}
\end{knitrout}
\caption{Illustration of the AnCred with Bayes factors procedure using the
  findings from the meta-analysis on the association of COVID-19 mortality and
  corticosteroids. The left plot shows the Bayes factor $\BF_{01}$ as a function
  of the relative variance $g$ of the sceptical prior. The result from the
  RECOVERY trial is challenged with a sceptical prior such that
  $\BF_{01} = 1/10$, for the other trials such a prior does not exist. The right
  plot shows the Bayes factor $\BF_{01}$ as a function of the relative mean
  $f = \mu/\hat{\theta}$ of the advocacy prior where the coefficient of
  variation from the prior is fixed to
  \mbox{$\text{CV} = \tau/\mu = 1/z(\gamma=1/3) = 0.67$}, where $z(\gamma)$ is
  given in \eqref{eq4:zgamma}. The RECOVERY and the CAPE COVID findings are
  challenged such that $\BF_{01} = 1/3$, for the other trials such a prior does
  not exist.}
\label{fig4:bf}
\end{figure}

@@

The plausibility of the sufficiently sceptical prior can be evaluated in light
of external evidence, but what should we do in the absence of such? We could
again use the \citet{Box1980} prior-predictive check as in
Section~\ref{sec4:IC}, however, the resulting tail probability is difficult to
compare to the Bayes-factor cut-off $\gamma$. When a specific alternative model
to the null is in mind, \citet[p. 391]{Box1980} also suggested to use a Bayes
factor for model criticism of the null model. Following this approach,
\citet{Pawel2020b} proposed to define a second Bayes factor contrasting the
sufficiently sceptical prior to an optimistic prior, which they defined as
\mbox{$\theta \given H_2 \sim \Nor(\hat{\theta}, \sigma^2)$} the posterior of
$\theta$ based on the data and the reference prior $f(\theta) \propto 1$. The
optimistic prior therefore represents the position of a proponent who takes the
original claim at face value. This leads to the second Bayes factor being
\begin{align}
  \label{eq4:bf12}
  \BF_{12} = \sqrt{\frac{2}{1 + g}} \cdot \exp\left\{-\frac{1}{2}\cdot \frac{z^{2}}{1 + g}\right\}.
\end{align}
Analogously to the tail probability approach from Section~\ref{sec4:IC},
intrinsic credibility is established if the data support the optimistic over the
sceptical prior at a higher level than they support the sceptical prior over the
null hypothesis, \ie{} if
\begin{align*}
  \BF_{12} \leq \BF_{01}
\end{align*}
with sufficiently sceptical relative prior variance $g$ from~\eqref{ggamma} used
in both Bayes factors. For example, if we challenge the RECOVERY trial finding
such that the resulting Bayes factor is only $\BF_{01} = 1/10$, we obtain
with~\eqref{eq4:sspv} the sufficiently sceptical relative prior variance
$g = 0.59$ and in turn with~\eqref{eq4:bf12} the Bayes factor $\BF_{12} = 1/64$,
so the finding is intrinsically credible at $\gamma = 1/10$.

@@

The right plot in Figure \ref{fig4:bf} illustrates application of the procedure
on data from the meta-analysis on association between COVID-19 mortality and
corticosteroids. The coefficient of variation of the advocacy prior is fixed to
$\text{CV} = 1/z(\gamma=1/3) = 0.67$ (for comparison, the CV of the advocacy
prior in traditional AnCred at $\alpha = 0.05$ is
$\text{CV} = 1/z_{\alpha/2}= 0.51$) and thus the Bayes factor $\BF_{01}$ only
depends on the relative mean $f = \mu/\hat{\theta}$. Under the sceptical prior
only the RECOVERY finding could be challenged at $\gamma = 1/3$ (where
$z(\gamma)=1.5$ corresponds to $\alpha=13$\%). With the advocacy prior this is
now also possible for the CAPE COVID finding \citep{Dequin2020}, where a prior
with mean $\mu = f \cdot \hat{\theta} = 0.37 \cdot (-0.79) = -0.29$ and standard
deviation $\tau = \text{CV} \cdot \mu = 0.2$ is able to make the finding
compelling at $\gamma = 1/3$. The corresponding prior credible interval for the
OR at level $1-\alpha$ ranges from 0.55 to 1, so advocates may still consider
the ``non-compelling'' finding as providing moderate evidence in favour of a
benefit, if external evidence supports mortality reductions in that range. Using
the prior-to-data conversion described in
Section~\ref{sec4:prior-data-translation}, the prior can be translated to a
trial with 69 events in both arms, but 206 non-events in the treatment and 182
non-events in the control arm (such that the mortality rate in the control arm
is the same as in the CAPE COVID trial). Note that the advocacy prior may not be
unique, \eg{} for the CAPE COVID finding the prior with relative mean
$f^\prime = 1.26$ and standard deviation $\tau^\prime = 0.67$ also renders the
data as just compelling at $\gamma = 1/3$. We recommend to choose the prior with
$f$ closer to zero, as it is the more conservative choice.
